Radio Emission from Red-Giant Hot Jupiters

### 2015-09-21 ms.tex
Minor edits to the abstract; adds a comment to the abstract.

\begin{abstract}
%%%
When planet-hosting stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a massive stellar wind.
Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.
We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and a proposed scaling for planetary magnetic fields.
We predict that RGHJs might be as bright as canonical hot Jupiters, and thus the low frequency radio emission from a RGHJ may be detectable at distances less than a few hundred parsecs with current/future instruments such as LOFAR and SKA.

>>>>

\begin{abstract}
%%%
When planet-hosting stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a massive stellar wind.
Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.
We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and a proposed scaling for planetary magnetic fields. \memoDS{I recommend nixing ``radiometric Bode's law'' from the abstract, but wanted to get others' opinions before doing so.}
We predict that RGHJs might be intrinsically brighter than canonical hot Jupiters, and thus the low frequency radio emission from a RGHJ may be detectable at distances up to a few hundred parsecs with current/future instruments such as LOFAR and the Square Kilometer Array.
